Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-05-13 paper/paper_main.tex
updating title

%\title{GravExplain: Demonstrating continuous gravitational wave searches using sound and a table-top interferometer}
\title{Title ideas...
\\\hspace{2em}\newline
Demonstrating continuous gravitational wave searches in the lab with an optical microphone
\\\hspace{2em}\newline
An optical microphone analogy to continuous gravitational wave searches 
\\\hspace{2em}\newline
Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone
\\\hspace{2em}\newline
}

>>>>

%\title{GravExplain: Demonstrating continuous gravitational wave searches using sound and a table-top interferometer}
\title{Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone}
